OpReg-Boost: Learning to Accelerate Online Algorithms \\ with Operator Regression

### 2021-01-16 paper/main.tex
added images

By definition $\hat{\tv}$ satisfies
\begin{equation}
	\norm{\hat{\tv} - \hat{\tv_i}} \leq \zeta \norm{\x - \x_i}, \quad \forall i \in I_{\ell},
\end{equation}
which implies that Lipschitz continuity (and contractivity) is preserved.

@@

Let $\xx$ be the vector stacking all the $\tv_{i,e}$, then the problem is equivalent to
\begin{align*}
	\min_{\xx} \psi(\xx) + \chi(\xx)
\end{align*}
where
$$
	\psi(\xx) = \frac{1}{2(\ell-1)} \norm{\xx - \y}^2 + \psi_1(\xx)
$$
with $\psi_1$ the indicator function imposing~\eqref{eq:interpolation-constraints} and $\xi$ the indicator function imposing the ``consensus'' constraints~\eqref{eq:consensus-constraints}. The problem can then be solved using the Peaceman-Rachford splitting (PRS) characterized by the following updates $\ell \in \mathbb{N}$:
\begin{subequations}
\begin{align}
	&\xx^j = \prox_{\rho \psi}(\z^j) \label{eq:prs-xi} \\
	&\vv^j = \prox_{\rho \chi}(2 \xx^j - \z^j) \\
	&\z^{j+1} = \z^j + \vv^j - \xx^j.
\end{align}
\end{subequations}
The proximal of $\chi$ corresponds to the projection onto the consensus space, and thus can be characterized simply by
$$
	\vv_{i,e}^j = \frac{1}{\ell-1} \sum_{e' | i \sim e'} \left( 2 \tv_{i,e'}^j - \z_{e'}^j\right).
$$
Regarding the proximal of $\psi$, $\psi$ is separable, in the sense that it can be written as
$$
	\psi(\xx) = \sum_{e \in \mathcal{V}} \left[ \frac{1}{2 (\ell-1)} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 + \iota_{e}(\tv_{i,e},\tv_{j,e}) \right]
$$
where $\iota_{e}$ denotes the indicator function of~\eqref{eq:interpolation-constraints} \andrea{is it $\psi_1$?}. Therefore, the update~\eqref{eq:prs-xi} can be solved by solving (possibly in parallel) the problems
\begin{equation}\label{eq:local-updates}
\begin{split}
	(\tv_{i,e},\tv_{j,e}) &= \argmin_{\tv_{i,e},\tv_{j,e}} \left\{ \frac{1}{2 (\ell-1)} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 + \right.\\ & \left.\qquad \frac{1}{2\rho} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \z_e^j}^2 \right\}\\
	&\text{s.t.} \quad \norm{\tv_{i,e} - \tv_{j,e}}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2.
\end{split}
\end{equation}
Problems~\eqref{eq:local-updates} are convex QCQP with one constraint, and can be solved in the dual domain as scalar problems by using Newton's method~\cite{.}, yielding a total computational complexity of $O(..)$ for the solution of~\eqref{.}.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width = 0.9\columnwidth]{Figures/comparison_projection_methods}
\caption{Comparison of feasibility and best approximation methods.}
\label{fig:projection_methods}
\end{figure}

As we can see, MAP is by far the fastest of the methods, reaching convergence (with tolerance $10^{-14}$) in just $33$ iterations. Parallel projections and Peaceman-Rachford splitting reach convergence in $1930$ and $1036$ iterations, respectively, while the best approximation methods are still far from converging after $50000$ iterations.

>>>>

By definition $\hat{\tv}$ satisfies
\begin{equation}\label{eq:lipschitz-interpolation}
	\norm{\hat{\tv} - \hat{\tv_i}} \leq \zeta \norm{\x - \x_i}, \quad \forall i \in I_{\ell},
\end{equation}
which implies that Lipschitz continuity (and contractivity) is preserved.

@@

Let $\xx$ be the vector stacking all the $\tv_{i,e}$, then the problem is equivalent to
\begin{align*}
	\min_{\xx} \psi(\xx) + \chi(\xx)
\end{align*}
where
$$
	\psi(\xx) = \frac{1}{2(\ell-1)} \norm{\xx - \y}^2 + \iota(\xx)
$$
\nicola{I renamed $\psi_1$ to $\iota$}

with $\iota(\xx) = \sum_{e \in \mathcal{V}} \iota_{e}(\tv_{i,e},\tv_{j,e})$ and $\iota_e$ the indicator function imposing~\eqref{eq:interpolation-constraints}, and $\chi$ the indicator function imposing the ``consensus'' constraints~\eqref{eq:consensus-constraints}. The problem can then be solved using the Peaceman-Rachford splitting (PRS) characterized by the following updates $\ell \in \mathbb{N}$:
\begin{subequations}
\begin{align}
	&\xx^j = \prox_{\rho \psi}(\z^j) \label{eq:prs-xi} \\
	&\vv^j = \prox_{\rho \chi}(2 \xx^j - \z^j) \\
	&\z^{j+1} = \z^j + \vv^j - \xx^j.
\end{align}
\end{subequations}
The proximal of $\chi$ corresponds to the projection onto the consensus space, and thus can be characterized simply by
$$
	\vv_{i,e}^j = \frac{1}{\ell-1} \sum_{e' | i \sim e'} \left( 2 \tv_{i,e'}^j - \z_{e'}^j\right).
$$
Regarding the proximal of $\psi$, $\psi$ is separable, in the sense that it can be written as
$$
	\psi(\xx) = \sum_{e \in \mathcal{V}} \left[ \frac{1}{2 (\ell-1)} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 + \iota_{e}(\tv_{i,e},\tv_{j,e}) \right].
$$
%where $\iota_{e}$ denotes the indicator function of~\eqref{eq:interpolation-constraints} \andrea{is it $\psi_1$?}.
Therefore, the update~\eqref{eq:prs-xi} can be solved by solving (possibly in parallel) the problems
\begin{equation}\label{eq:local-updates}
\begin{split}
	(\tv_{i,e},\tv_{j,e}) &= \argmin_{\tv_{i,e},\tv_{j,e}} \left\{ \frac{1}{2 (\ell-1)} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 + \right.\\ & \left.\qquad \frac{1}{2\rho} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \z_e^j}^2 \right\}\\
	&\text{s.t.} \quad \norm{\tv_{i,e} - \tv_{j,e}}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2.
\end{split}
\end{equation}
Problems~\eqref{eq:local-updates} are convex QCQP with one constraint, and can be solved in the dual domain as scalar problems by using Newton's method~\cite{.}, yielding a total computational complexity of $O(..)$ for the solution of~\eqref{.}.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width = 0.9\columnwidth]{Figures/comparison_projection_methods}
\caption{Comparison of feasibility and best approximation methods. \nicola{modified the figure to have markers}}
\label{fig:projection_methods}
\end{figure}

As we can see, MAP is by far the fastest of the methods, reaching convergence (with tolerance $10^{-14}$) in just $30$ iterations. Parallel projections and Peaceman-Rachford splitting reach convergence in $2161$ and $1158$ iterations, respectively, while the best approximation methods are still far from converging after $50000$ iterations.
